### 2014-07-18 tex/proofs.tex
Added proof for constraint mutual exclusion.

\begin{theorem}
\label{thm:mutex}
If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$ that is equivalent to some set of lazy states $\zeta$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, and any two pairs $(\phi_\alpha\ l_\alpha) &\in \cfgnt{L}_s(r)$ and $(\phi_\beta\ l_\beta) &\in \cfgnt{L}_s(r)$ such that $l_\alpha &\ne l_\beta$,
%\begin{align*}
%(\phi_\alpha\ l_\alpha) &\in \cfgnt{L}_s(r)\\
%(\phi_\beta\ l_\beta) &\in \cfgnt{L}_s(r)\\
%l_\alpha &\ne l_\beta
%\end{align*}
the following predicate is valid
$$\neg (\phi_s \wedge \phi_\alpha \wedge \phi_\beta)$$
\end{theorem}
\begin{proof}
\end{proof}

>>>>

\begin{theorem}
\label{thm:mutex}
If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, and any two pairs $(\phi_\alpha\ l_\alpha) &\in \cfgnt{L}_s(r)$ and $(\phi_\beta\ l_\beta) &\in \cfgnt{L}_s(r)$ such that $l_\alpha &\ne l_\beta$, then
%\begin{align*}
%(\phi_\alpha\ l_\alpha) &\in \cfgnt{L}_s(r)\\
%(\phi_\beta\ l_\beta) &\in \cfgnt{L}_s(r)\\
%l_\alpha &\ne l_\beta
%\end{align*}
$$(\phi_\alpha \wedge \phi_\beta) = \cfgt{false}$$
\end{theorem}
\begin{proof}
The proof will proceed inductively. For the base case, consider any initial state $s_0$. The property holds by construction. (Hands waving around in the air for emphasis)

Now we will show that if the exclusivity property holds for some state $s_s$, then it holds for any state $s_s^\prime$ where $s_s \rightarrow_s s_s^\prime$.

First, suppose we have state $s_s$ and intermediate state $s_s^\prime$ where $s_s \rightarrow_S s_s^\prime$. If all fields are initialized, then $s_s$ and $s_s^\prime$ are identical, so the property holds for $s_s^\prime$. If any field is uninitialized, then the fields are initialized to new references, for which the exclusivity property holds by construction. (Hands waving around in the air for emphasis)

Since the exclusivity property holds for every intermediate state, for any instruction that relies on the summary machine we can assume without loss of generality that all pertinent fields are initialized.

Now, suppose we have a field read instruction. When we read the field, a new value set is created based on the $\mathbb{VS}$ function. The members of the value set have the form $(\phi\wedge \phi^\prime\ \ l)$. Choose any two distinct members of the value set, $(\phi_\alpha \wedge \phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge \phi_\beta^\prime\ \ l_\beta)$. If $\phi_\alpha \ne \phi_\beta$, we know that exclusivity holds because $\phi_\alpha$ and $\phi_\beta$ came from the same value set in $s_s$, and are therefore exclusive. If $\phi_\alpha = \phi_\beta$, we know that exclusivity holds because $\phi_\alpha^\prime$ and $\phi_\beta^\prime$ came from the same value set in $s_s$ and are therefore exclusive. Thus, the exclusivity property holds for any pair of constraints in the value set. Since the only new value set in $L_{s^\prime}^\rightarrow$ is generated by the $\mathbb{VS}$ function, we are guaranteed that if exclusivity holds for $s_s$, then exclusivity holds for $s_s^\prime$.

Suppose we have a field write instruction. This case is nearly identical as the field read. In this instruction, a new value set is created. The members of the value set have the form $(\phi\wedge \phi^\prime\ \ l)$. Choose any two distinct members of the value set, $(\phi_\alpha \wedge \phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge \phi_\beta^\prime\ \ l_\beta)$. If $\phi_\alpha \ne \phi_\beta$, we know that exclusivity holds because $\phi_\alpha$ and $\phi_\beta$ came from the same value set in $s_s$, and are therefore exclusive. If $\phi_\alpha = \phi_\beta$, we know that exclusivity holds because $\phi_\alpha^\prime$ and $\phi_\beta^\prime$ came from the same value set in $s_s$ and are therefore exclusive. Thus, the exclusivity property holds for any pair of constraints in the value set. Since exclusivity holds for the only new value set in $L_{s^\prime}^\rightarrow$, we are guaranteed that if exclusivity holds for $s_s$, then exclusivity holds for $s_s^\prime$.

Suppose we have a "new" instruction. In this case, only one value set is added to $L_{s^\prime}^\rightarrow$, and that value set contains only one member, so exclusivity holds by default.

Suppose we have any instruction other that a read, write, or new. No machine rule other than those three listed instructions modifies the $L$ function. Therefore, the exclusivity property must hold for $s_s^\prime$ in these cases.

Since the exclusivity property holds for any initial state, and since it holds for any "next" state if the property holds for the previous state, we have proven the property for every symbolic state.
\end{proof}
